Circularity in Population-Based FA Analysis

### 2011-10-17 ANTsTBSS/paper.tex
ENH: Adding revision stuff

Caveats with our analysis include a lack of ground truth in the
clinical component of the study.   Additionally, we are not addressing
the biological plausibility or our results nor do we
intend to (in this paper) enter into discussion on the mechanisms of
TBI, gender difference and DTI that may lead to the detected results.
Rather, we focus on the technical issue of circularity caused by
normalizing the image feature of interest with functions that maximize
the statistic used in hypothesis testing.  We also cannot argue that our analysis
invalidates previous studies in which circularity might be an issue.  
Finally, we do not address the very promising work concerning
whole tensor DTI normalization \citep{Zhang2007,Hecke2007}, DTI template-based
strategies \citep{Mori2009,Hecke2011}, {\color{red}{or other related methods \cite{jbabdi2010}}}.  Although investigation is beyond the scope
of this work, these whole-tensor approaches might provide the necessary
anatomical information to overcome the deficiencies addressed in this
work.

>>>>

Caveats with our analysis include a lack of ground truth in the
clinical component of the study.   Additionally, we are not addressing
the biological plausibility of our results nor do we
intend to (in this paper) enter into discussion on the mechanisms of
TBI, gender difference and DTI that may lead to the detected results.
Rather, we focus on the technical issue of circularity caused by
normalizing the image feature of interest with functions that maximize
the statistic used in hypothesis testing.  We also cannot argue that our analysis
invalidates previous studies in which circularity might be an issue.  
Finally, we do not address the very promising work concerning
whole tensor DTI normalization \citep{Zhang2007,Hecke2007}, DTI template-based
strategies \citep{Mori2009,Hecke2011}, {\color{red}{or other related methods \cite{jbabdi2010}}}.  Although investigation is beyond the scope
of this work, these whole-tensor approaches might provide the necessary
anatomical information to overcome the deficiencies addressed in this
work.
